Response to the defense feedback

### 2021-06-18 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch. Researchers~\cite{bernstein2008chacha,langley2016chacha20} design and implement new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks. Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.  Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which encompasses formal verification methods to design, analyze and implement the cryptography libraries. Formal verification on side-channel leakages starts with a leakage model, which abstracts what an attacker can observe during an attack. After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that observations are independent of the input secrets. The property is an example of \textit{noninterference} or \textit{secure information flow}. However, achieving noninterferecne for real-world software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).

\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU). A straightforward way to defend these attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}. For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and these VMs share the same last-level cache (LLC). Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}.
\subsubsection*{Randomization}
This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information. For example, Random Permutation Cache ~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process. Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.

>>>>

\subsubsection*{New Implementation}
Recent work~\cite{bernstein2012security,libsodium,zinzindohoue2017hacl,monocypher} proposes to design and implement clean-slate side-channel free libraries from scratch. Researchers~\cite{bernstein2008chacha,langley2016chacha20} design and implement new constant-time cryptographic algorithms (e.g., ChaCha20) to defend against timing side-channel attacks. Unfortunately, writing side-channel resistant cryptography code and validating the security property can be tedious and error-prone.  Computer-aided cryptography~\cite{barbosa2021sok} is proposed to address the challenge, which encompasses formal verification methods to design, analyze and implement the cryptography libraries. Formal verification on side-channel leakages starts with a leakage model, which abstracts what an attacker can observe during an attack. After defining a leakage model, the implementation is secure (under the leakage model) to side-channel attacks if and only if it can be proved that observations are independent of the input secrets. The property is an example of \textit{noninterference} or \textit{secure information flow}. Eldib et al.~\cite{eldib2014smt} propose using a SMT solver based method to formally verifying masked implementations. Bayrak et al.~\cite{bayrak2013sleuth} verify power-based side-channel countermeasures.  However, achieving noninterferecne for real-world software is often impractical and researchers also seek to compromised solutions such as quantitative information flow (see Section~\ref{sec:qif}).

\subsection{Hardware Countermeasures}
\subsubsection*{Resource Partitioning}
Side-channel attacks usually require attackers and victims to share some hardware resources (e.g., CPU cache, MMU). A straightforward way to defend these attacks is to partition the resources and ensure the attacker and the victim never share the same hardware resource~\cite{Page2005PartitionedCA,shi2011limiting,liu2016catalyst}. For example, in a cloud computing environment, several virtual machines (VMs) can be hosted on the same physical machine and these VMs share the same last-level cache (LLC). Researchers proposed different methods to partition the LLC such as cache coloring~\cite{shi2011limiting}, using Intel Cache Allocation Technology~\cite{liu2016catalyst}. Recent work also uses machine checkable methods to verify side-channel resistance in hardware~\cite{Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,236334}.
\subsubsection*{Randomization}
This type of defense randomizes the behaviors of hardware resources to make it harder for attackers to infer secrets based on side-channel information. For example, Random Permutation Cache ~\cite{wang2007new} uses a dynamically randomized memory to cache mapping table for each different process. Vattikonda et al.~\cite{vattikonda2011eliminating} add noises to the result of the system timer to mitigate timing-based channels.
